Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-23 prop_iop.tex
prop_iop.tex \section{Cryptodeterministic Measures} Starting...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quantum Interval-valued Probability Measures}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}

@@

\section{Cryptodeterministic Measures}

A real or interval-valued probability is a way to model our belief
whether an event will happen or not. Classically, when we toss a coin
or throw a needle, if we know all the initial condition, we can determine
whether an event happens or not for sure~\cite{DiaconisHolmesMontgomery2007}.

\newpage{}

One obvious way to discretize probability is to only consider a finite
set of probability values. For example, instead of $\left[0,1\right]$,
we only consider the probability $\check{\mathscr{L}}$ to be two
values $\left\{ 0,1\right\} $, three values $\left\{ 0,\frac{1}{2},1\right\} $,
or any finite set $\check{\mathscr{L}}\subset\left[0,1\right]$. Then,
a finite value classical probability distribution is a function $\check{\mathcal{Q}}:\Omega\rightarrow\check{\mathscr{L}}$
with 
\begin{equation}
\sum_{i=0}^{d-1}\check{\mathcal{Q}}\left(\omega_{i}\right)=1\textrm{ .}
\end{equation}
For example, a classical probability distribution for a fair coin
is $\check{\mathcal{Q}}\left(H\right)=\check{\mathcal{Q}}\left(T\right)=\frac{1}{2}$.
Because $\check{\mathcal{Q}}$ only takes value $\frac{1}{2}$, we
can pick $\check{\mathscr{L}}=\left\{ \frac{1}{2}\right\} $.

A finite value quantum probability distribution $\check{\mathcal{P}}:\C^{d*}\rightarrow\check{\mathscr{L}}$
can be defined similarly with 
\begin{equation}\eqalign{ 
{\displaystyle \sum_{i=0}^{d-1}\check{\mathcal{P}}\left(\ket{i}\right)=1}\textrm{ for any orthonormal basis }\left\{ \ket{i}\right\} _{i=0}^{d-1}\textrm{ ;}\label{eq:total-probability-CQT-1}\\
\check{\mathcal{P}}\left(\ket{\Phi}\right)=\check{\mathcal{P}}\left(\lambda\ket{\Phi}\right)\textrm{ for }\lambda\in\C^{*}=\C\backslash\left\{ 0\right\} \textrm{ .}\label{eq:parallel-CQT-1} 
}\end{equation} 
Although it seems that the definition is almost the same as the one
in $\left[0,1\right]$-valued, actually this lead to the well-known
Kochen-Specker theorem.

\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}For
$d\ge3$, there is no $\left\{ 0,1\right\} $-valued quantum probability
distribution.\end{thm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Quantum Interval-valued Probability Measures}
